|

### 2024-08-11 doc/paper.qmd
update latex tables

def prep_latex_table(df, caption=None, label=None, fontsize='\\fontsize{11}{13}\\selectfont'):
    df = escape_special_characters(df.reset_index())
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)
    latex_table = df.to_latex(
        column_format=column_format,
        index=False,
        float_format=custom_float_format,
    )
    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        fontsize,  # Set font size for the table
        latex_table,
        f"\\caption{{{caption}}}" if caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - EM1, EM2, EM3, EM4, Aggregate EM Score, and Summary Statistics',
    label='tab:final_combined_table'
))
```

@@

print(prep_latex_table(
    results['table_1'],
    caption='Replicated table - Number of Firm-Year Observations per Country',
    label='tab:table_1'
))
```

>>>>

def prep_latex_table(df, caption=None, label=None, fontsize='\\fontsize{11}{13}\\selectfont'):
    df = escape_special_characters(df.reset_index(drop=True))  # Drop the index column from output tables for better readability
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)
    latex_table = df.to_latex(
        column_format=column_format,
        index=False, 
        float_format=custom_float_format,
    )
    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        fontsize,  # Set font size for the table
        latex_table,
        f"\\caption{{{caption}}}" if caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - Country scores for earnings management measures (Sorted by aggregate earnings management)',
    label='tab:final_combined_table'
))
```

@@

print(prep_latex_table(
    results['table_1'],
    caption='Replicated table - Descriptive statistics: Number of firm-year observations per country',
    label='tab:table_1'
))
```
